
\begin{frame}{Research focus}

\begin{itemize}
	\item Direct comparison of two hypotheses re onset-latency slowdown for conjoined NPs.
	\item[i.] \uncover<2->{Phrase scope obligated by the production system, leading to a systematic slowdown.}
	\item[ii.] \uncover<3->{Preplanning beyond the first noun is more likely for conjoined NPs but not obligated by the production system.} 
	\item \uncover<4>{Implementation of both hypotheses as statistical models in Stan \parencite{carpenter2017stan}; code based on \textcite{sorensen2016bayesian} and \textcite{vasishth2017}; also \textcite{vasishth2017feature}.}

\end{itemize}

\end{frame}


\begin{frame}{Pooled re-analysis of 8 experiments}



\begin{itemize}
	\item \textcite{hardy2019age}: 90 ppts; 36 items
	\item \textcite{hardy2020healthy}: 105 ppts; 80 items
	\item \textcite{martin2010planning}: 3$\times$12 ppts; 2$\times$48 and 1$\times$64 items
	\item \textcite{roeser2019advance}: 3$\times$32 ppts; 96 items 
\end{itemize}

\vfill 
\begin{itemize}
	\item 2 conditions
	\item[a.] \textbf{Conjoined NPs:} \textit{The boy and the dog moved above the kite.}
	\item[b.] \textbf{Simple NPs:} \textit{The boy moved above the dog and the kite.}
\end{itemize}


\end{frame}




\begin{frame}[fragile]{Pooled Linear Mixed Effects Model (null hypothesis)}
	
		\begin{equation*}
			\begin{aligned}	
				y_{ijk} \sim LogNormal(\mu_{ijk}, \sigma_{e_k}^2) \\
				\mu_{ijk} = \alpha_k + u_i + w_j
			\end{aligned}
		\end{equation*}
		\begin{small}	
			\begin{itemize}
				\item Non-centred mean $\alpha_k$ each for $k = 1, \dots, K$ where $K$ is the number of studies \parencite{gelman2014} with pooled latency $\alpha_{\mu}$.
				
				\item Participants: $u_i \sim Normal(0, \sigma_u^2)$
				\item Items: $w_j \sim Normal(0, \sigma_w^2)$

				\item Pooled error variance $\sigma_e^2$
%				\item $\alpha_k$ is the latency coefficient for the $k$th study.
%				\item $\alpha_{\mu}$ is the pooled latency coefficient.
%				\item Non-centred parametrisation for $\alpha_k$ \parencite{gelman2014}.
			\end{itemize}
		\end{small}
\end{frame}


\begin{frame}[fragile]{Pooled Linear Mixed Effects Model}
			
	\begin{equation*}
		\begin{aligned}	
			y_{ijk} \sim LogNormal(\mu_{ijk}, \sigma_{e_k}^2)\\
			\only<1>{\mu_{ijk} = \alpha_k + \mathcolorbox{red!20!white}{\beta_k \cdot x_{[0,1]}} + u_i + w_j\\}
		\end{aligned}	
	\end{equation*}		
	\begin{small}	
		\begin{itemize}
%			\item $\beta_k$ is the latency change for conjoined NPs for the $k$th study.
			\item $x=0$ for simple NPs; $x=1$ for conjoined NPs.
			\item $\beta_k$: by-study NP difference with pooled effect $\beta_{\mu}$. 
%			\item $\beta_{\mu}$ is the pooled latency change for conjoined NPs.
			\item \textbf{Conceptual idea:} 
			\item[$\bullet$] Underlying process can be characterised as \textbf{one distribution}. 
			\item[$\bullet$] Deterministic syntax-driven model: conjoined NPs slow down preplanning by $\beta$ msecs.
		\end{itemize}
	\end{small}
	
\end{frame}


\begin{frame}[fragile]{Pooled Mixture of Gaussians}
	
	\begin{equation*}
		\begin{aligned}
	\only<1>{y_{ijk} \sim \theta_{{NP}_k} \cdot LogNormal(\mu_{ijk} + \delta_k, \sigma_{e'_k}^2) + \\
(1 - \theta_{{NP}_k}) \cdot LogNormal(\mu_{ijk}, \sigma_{e_k}^2) \\}
	\only<2>{y_{ijk} \sim \theta_{{NP}_k} \cdot LogNormal(\mu_{ijk} + \delta_k, \sigma_{e'_k}^2) + \\
	(1 - \theta_{{NP}_k}) \cdot \mathcolorbox{red!20!white}{LogNormal(\mu_{ijk}, \sigma_{e_k}^2)} \\}
	\only<3>{y_{ijk} \sim \theta_{{NP}_k} \cdot \mathcolorbox{red!20!white}{LogNormal(\mu_{ijk} + \delta_k, \sigma_{e'_k}^2)} + \\
	(1 - \theta_{{NP}_k}) \cdot LogNormal(\mu_{ijk}, \sigma_{e_k}^2) \\}
	\only<4->{y_{ijk} \sim \mathcolorbox{red!20!white}{\theta_{{NP}_k}} \cdot LogNormal(\mu_{ijk} + \delta_k, \sigma_{e'_k}^2) + \\
	(1 - \theta_{{NP}_k}) \cdot LogNormal(\mu_{ijk}, \sigma_{e_k}^2) \\}
			\mu_{ijk} = \alpha_k + u_i + w_j\\
		\end{aligned}
	\end{equation*}

	\begin{small}
		\begin{itemize}
			\item \textbf{Conceptual idea:}
			\only<-4>{\item[$\bullet$] Underlying process is \textbf{mixture of two distributions}:
			\item[i.] \uncover<2->{onset latency with variance $\sigma_{e_k}^2$ }
			\item[ii.] \uncover<3->{slowdown $\delta$ with larger variance $\sigma_{e'_k}^2$}  
			\item[$\bullet$] \uncover<4->{$\theta$ captures the probability of long latencies by NP type.}}
			\only<5>{
			\item[$\bullet$] Planning beyond first noun is possible for both NP types resulting in a slowdown $\delta$.
			\item[$\bullet$] Non-deterministic model: planning beyond the first noun is more likely for conjoined NPs reflected in larger probability of long onset latencies $\theta$.
			}
		\end{itemize}
	\end{small}		
	
\end{frame}



\begin{comment}
\begin{frame}{Predictions}

\begin{itemize}
	\uncover<-1>	{\item Standard analysis (LMM): Conjoined NPs cause a systematic slowdown in onset latencies, implying that phrase syntax is obligated by the production system.}
	\uncover<2>	{\item Alternative analysis (MoG): Conjoined NPs show a larger probability for longer onset latencies which, however, remain the minority; hence, preplanning syntax is not obligated by the production system.}
\end{itemize}

\end{frame}
\end{comment}



